---
title: "Nordnorsk_ERP data analysis"
output: html_notebook
---

#### Here we will analyze the results of the Nordnorsk behavioural data  
First, we will do some data wrangling to clean up the data. 

```{r}
#First we will load packages
library(tidyverse)
library(lme4)
library(afex)
library(ggplot2)
library(sjmisc)
library(dplyr)
library(cocor)
library(readxl)
library(emmeans)
library(MuMIn)
library(DHARMa)
library(ggpubr)
library(sjPlot)
library(LMERConvenienceFunctions)
library(performance)
library(glmmTMB)
library(TMB)
library(here)
library(stringr)
```

#### Here we will analyze the results of the Nordnorsk ERP data 
First, we will do some data wrangling to clean up the data. 

```{r}
setwd("~/Dropbox/Postdoc-UiT/NordNorsk/Data Analysis")
#read data 
data_erp<-read_excel("nordnorskERP.xlsx")#ERP data
lsbq_erp<-read_excel("lsbq_data_S122.xlsx")#LSBQ composite score background data 
group_info<-read_excel("nordnorsk_groups_S122.xlsx") #Native speaker status data 

#merge two data sets 
erp_all1<-merge(group_info, lsbq_erp, by = "Subject")
erp_all<-merge(erp_all1, data_erp, by = "Subject")

#rename variables
erp_all_sep<-erp_all%>%
  mutate(Condition = dplyr::recode(Condition,NumGr ="NUM_nonagr", NumUg = "NUM_agr", GenGr = "GEN_agr", GenUg = "GEN_nonagr"))%>%
  dplyr::rename(Agreement = Condition)%>%
  dplyr::rename(Amplitude = Voltage)

#for combined data analysis 
erp_com<-erp_all%>%
  mutate(Agreement = Condition)%>%
  mutate(Num_Gen = Condition)%>%
  mutate(Agreement = dplyr::recode(Agreement,NumGr ="non-agreement", NumUg = "agreement", GenGr = "agreement", GenUg = "non-agreement"))%>%
  mutate(Num_Gen = dplyr::recode(Num_Gen,NumGr ="number", NumUg = "number", GenGr = "gender", GenUg = "gender"))%>%
  dplyr::rename(Amplitude = Voltage)

#create data frame by filtering out P from Trondheim and Bergen 
filterdata<- c("S86","S94","S97","S121")

#filter Trondheim and Bergen data in the combined file 
erp_com<-erp_com%>%
  filter(!Subject%in%filterdata)

length(unique(erp_com$Subject))# 105 


####### This analysis is for excluding those who have only 50% retainment of EEG data####### 
#create data frame by filtering out P with missing data 
#missing_data<- c("P06","S01" ,"S05", "S07", "S08", "S09", "S11", "S14","S16","S18", "S19", "S20", "S21", "S25", "S26", "S28", "S30", "S31", "S32", "S37", "S38", "S39", "S40", "S41", "S42", "S45", "S50", "S51", "S52", "S55", "S57", "S58", "S61", "S63", "S68", "S70")#-33 participants

#filter missing data in the combined file 
#erp_com<-erp_com%>%
#filter(!Subject%in%missing_data)


```

## Gender and Number ERP analysis 
We will now run lmer with Num_Gen (Gender,Number), Agreement (agreement,non-agreement), Composite score on the LSBQ (higher values indicate more exposure to NN), Group (non-native NN, native NN)
```{r}
#let's first analyze P600 effect for both by filtering for P6 window 
erp_all_2<-erp_com%>%
  filter(Window == "P6")%>%
  filter(Num_Gen == "number"|Num_Gen == "gender")%>%
  mutate(composite_c = scale(composite))%>%
  filter(Amplitude > -10)#remove weird clustering of data coming from 3 participants 

#First we will run a lmer model to do some model diagnostic 
c1<-lmer(Amplitude~Agreement*Num_Gen*composite_c*Group+ROI+(1|Electrode)+(1|Subject),data=erp_all_2)
summary(c1)
#model diagnostic
sjPlot::plot_model(c1, type='diag')#some outliers need to be removed but overall the model assumptions look good 
#remove outliers 
erp_all_3<-romr.fnc(c1, erp_all_2, trim = 3)$data#111 data points are removed 

#run LRT with afex package with the new outlier removed data  
library(afex)
c2<-mixed(Amplitude~Agreement*Num_Gen*composite_c*Group+ROI+(1|Electrode)+(Agreement+Num_Gen|Subject),data=erp_all_3,method = "LRT")
c2#ANOVA table
summary(c2)#summary output 


library(emmeans)
#post-hoc comparisons to see the effect of Agreement differences between Number and Gender
con2<-emmeans(c2, ~ Agreement*Num_Gen, test = "Tukey")
contrast(con2, interaction ="pairwise")

#post-hoc comparisons to see the effect of Agreement on Number and Gender separately
con1<-emmeans(c2, ~ Agreement|Num_Gen, test = "Tukey")
contrast(con1, interaction ="pairwise")

#post-hoc comparisons to see the effect of Agreement and Group on Number and Gender separately
con3<-emmeans(c2, ~ Agreement*Group|Num_Gen, test = "Tukey")
contrast(con3, interaction ="pairwise")


######VISUALIZATION######### 
#run model with lmer for the sake of visualization (since c1 model run with the afex package is not compatible with sjPlot)
c3<-lmer(Amplitude~Agreement*Num_Gen*composite_c*Group+ROI+(1|Electrode)+(Agreement+Num_Gen|Subject),data=erp_all_3)
summary(c3)
#plot model for the 2 way-interaction
sjPlot::plot_model(c3, type = "pred", terms = c( "Num_Gen","Agreement"))
#plot model for the 3 way-interaction
sjPlot::plot_model(c3, type = "pred", terms = c( "Num_Gen","Agreement","Group"))
sjPlot::plot_model(c3, type = "pred", terms = c("composite_c", "Agreement", "Num_Gen"))
#plot model for the 4 way-interaction with raw data points 
sjPlot::plot_model(c3, type = "pred", terms = c("composite_c", "Agreement", "Group","Num_Gen"),show.data = TRUE, jitter = 0.1)
#plot model for the 4 way-interaction without raw data points
sjPlot::plot_model(c3, type = "pred", terms = c("composite_c", "Agreement", "Group","Num_Gen"))


```

## Gender ERP analysis 
We will now run lmer Agreement (agreement,non-agreement), Composite score on the LSBQ (higher values indicate more exposure to NN), Group (non-native NN, native NN) as fixed factors as well as their interactions for Gender only
```{r}
#let's first analyze P600 effect for both by filtering for P6 window for gender
erp_all_gen<-erp_com%>%
  filter(Window == "P6")%>%
  filter(Num_Gen == "gender")%>%
  mutate(composite_c = scale(composite))
  #filter(Amplitude > -10)#remove weird clustering of data coming from 3 participants 

#First we will run a lmer model to do some model diagnostic 
g1<-lmer(Amplitude~Agreement*composite_c*Group+ROI+(1|Electrode)+(1|Subject),data=erp_all_gen)
summary(g1)

#model diagnostic
sjPlot::plot_model(g1, type='diag')#some outliers need to be removed but overall the model assumptions look good 
#remove outliers 
erp_all_gen_2<-romr.fnc(g1, erp_all_gen, trim = 3)$data#37 data points are removed 

#run LRT with afex package with the new outlier removed data  
library(afex)
g2<-mixed(Amplitude~Agreement*composite_c*Group+ROI+(1|Electrode)+(Agreement|Subject),data=erp_all_gen_2,method = "LRT")
g2#ANOVA table
summary(g2)#summary output 


###VISUALZATION###
g3<-lmer(Amplitude~Agreement*composite_c*Group+ROI+(1|Electrode)+(Agreement|Subject),data=erp_all_gen)
summary(g3)
sjPlot::plot_model(g3, type = "pred", terms = c("composite_c", "Agreement", "Group"))
sjPlot::plot_model(g3, type = "pred", terms = c("Agreement", "Group"))
sjPlot::plot_model(g3, type = "pred", terms = c("composite_c", "Agreement"))
```

## Number ERP analysis 
We will now run lmer Agreement (agreement,non-agreement), Composite score on the LSBQ (higher values indicate more exposure to NN), Group (non-native NN, native NN) as fixed factors as well as their interactions for Number only
```{r}
#let's first analyze P600 effect for both by filtering for P6 window for number
erp_all_num<-erp_com%>%
  filter(Window == "P6")%>%
  filter(Num_Gen == "number")%>%
  mutate(composite_c = scale(composite))%>%
  filter(Amplitude > -10)#remove weird clustering of data coming from 3 participants 

#First we will run a lmer model to do some model diagnostic 
n1<-lmer(Amplitude~Agreement*composite_c*Group+ROI+(1|Electrode)+(1|Subject),data=erp_all_num)
summary(n1)

#model diagnostic
sjPlot::plot_model(n1, type='diag')#some outliers need to be removed but overall the model assumptions look good 
#remove outliers 
erp_all_num_2<-romr.fnc(n1, erp_all_num, trim = 3)$data#52 data points are removed 

#run LRT with afex package with the new outlier removed data  
library(afex)
n2<-mixed(Amplitude~Agreement*composite_c*Group+ROI+(1|Electrode)+(1|Subject),data=erp_all_num,method = "LRT")
n2#ANOVA table
summary(n2)#summary output 


###VISUALZATION###
n3<-lmer(Amplitude~Agreement*composite_c*Group+ROI+(1|Electrode)+(1|Subject),data=erp_all_num)
summary(n3)
sjPlot::plot_model(n3, type = "pred", terms = c("composite_c", "Agreement", "Group"))

```


### Here, will check particpants who had larger amplitutde for number agreement### 

```{r}
recall_p<-erp_all_2%>%
  filter(Num_Gen == "number")%>%
  dplyr::group_by(Subject, Agreement, Group, composite)%>%
  dplyr::summarize(meanAmp = mean(as.numeric(Amplitude)))%>%
  spread(Agreement, meanAmp)%>%
  mutate(P600 = agreement - `non-agreement`)%>%
  arrange(P600)%>%
  filter(P600 > 0)%>%
  arrange(composite)
  #group_by(Group)%>%
  #tally()

#write.csv(recall_p, "follow-up_bokmål_subjects.csv")

```


#### Here we will analyze the results of the Nordnorsk behavioural data 

```{r}

#read csv
behav_all<-read_csv("behavioural_data_all.csv")

#filter Trondheim and Bergen data in the combined file 
behav_all<-behav_all%>%
  filter(!Subject%in%filterdata)

length(unique(behav_all$Subject))#four data missing due to technical bluetooth problems for behavioural data 

#subset data to gender and number 
behav_sub<-behav_all%>%
  filter(Condition == "gender_g"  | Condition == "gender_u" | Condition == "num_g"| Condition == "num_u")%>%
  mutate(Agreement = recode(Condition, gender_g = "agreement", gender_u = "non-agreement",num_g = "non-agreement", num_u = "agreement"))%>%
  mutate(Num_Gen = recode(Condition, gender_g = "gender", gender_u = "gender",num_g = "number", num_u = "number"))%>%
  mutate(composite_c = scale(composite))%>%
  mutate_if(is.character, as.factor)

##Descriptive Stats##

#summarize per condition RT
RT_behav<-behav_sub%>%
  mutate(RT =as.numeric(RT))%>%
  dplyr::group_by(Num_Gen, Agreement)%>%
  dplyr::summarise(meanRT = round(mean (RT), digits = 0)/10, sdRT = round (sd (RT), digits = 0)/10, seRT = round(sd(RT) / sqrt(length(RT)), digits = 0)/10)

behav_sub%>%
  mutate(RT =as.numeric(RT))%>%
   dplyr::group_by(Num_Gen, Agreement)%>%
  dplyr::summarise(meanRT = mean (RT), sdRT = sd (RT),seRT = sd(RT) / sqrt(length(RT)))


#summarize per condition Accuracy
Accuracy_behav<-behav_sub%>%
  drop_na()%>%
  dplyr::group_by(Num_Gen, Agreement)%>%
  dplyr::summarise(meanAccuracy = round(mean (Accuracy), digits = 2), sdAccuracy = round(sd (Accuracy), digits = 2) ,seAccuracy = round (sd(Accuracy) / sqrt(length(Accuracy)), digits = 2))

behav_sub%>%
  group_by(Num_Gen, Agreement)%>%
  drop_na()%>%
  dplyr::summarise(meanAccuracy = mean (Accuracy), sdAccuracy = sd (Accuracy),seAccuracy = sd(Accuracy) / sqrt(length(Accuracy)))

```


### Here we will visualize the descriptive results of accuracy and reaction time for gender and number 
```{r}
#summary of the data frame 
summary(behav_sub)

##Plot Accuracy
acc_plot<-Accuracy_behav%>%
  ggplot(aes(x= Num_Gen,y= meanAccuracy, fill = Agreement))+geom_bar(stat="identity", position="dodge")+geom_errorbar(aes(ymin=meanAccuracy-seAccuracy, ymax=meanAccuracy + seAccuracy),width=.6, position=position_dodge(.9))+xlab("Condition")+ylab("Proportion of acceptance")+ geom_text(aes(label = paste(format(meanAccuracy, nsmall = 2), "")), vjust = 2, position = position_dodge(.9))+ ggtitle("Acceptance")+ geom_text(aes(label = paste(format(sdAccuracy, nsmall = 1) ,"SD")), vjust = 3.5, position = position_dodge(.9))

##Plot Reaction time 
rt_plot<-RT_behav%>%
  ggplot(aes(x= Num_Gen,y= meanRT, fill = Agreement))+geom_bar(stat="identity", position="dodge")+geom_errorbar(aes(ymin=meanRT-seRT, ymax=meanRT + seRT),width=.6, position=position_dodge(.9))+xlab("Condition")+ylab("Reaction Time")+ geom_text(aes(label=  paste(format(meanRT, nsmall = 2), "ms")), vjust = 2, position = position_dodge(.9))+ ggtitle("RT")+ geom_text(aes(label = paste(format(sdRT, nsmall = 1) ,"SD")), vjust = 3.5, position = position_dodge(.9))

#Combine two plots

fig1<-ggarrange(acc_plot,rt_plot,
                    ncol = 1, nrow = 2,
           common.legend = TRUE, legend = "right"
          )

ggsave(filename = "Figure1",device='jpeg', dpi=300)
```

## Gender and Number behavioural analysis 
We will now run glmer for accuracy and lmer for reaction time data with Num_Gen (Gender,Number), Agreement (agreement,non-agreement), Composite score on the LSBQ (higher values indicate more exposure to NN), Group (non-native NN, native NN)

#### Accuracy Analysis 
```{r}
##Accuracy Run Analysis## 

#First we will run a glmer model to do some model diagnostic 
b1<-glmer(Accuracy~Agreement*Num_Gen*composite_c*Group+(Agreement+Num_Gen|Subject),data=behav_sub,family='binomial',control = glmerControl(optimizer = "bobyqa"))
summary(b1)

#model diagnostic
sjPlot::plot_model(b1, type='diag')#looks good 

#run LRT with afex package with the new outlier removed data  
library(afex)
b2<-mixed(Accuracy~Agreement*Num_Gen*composite_c*Group+(Agreement+Num_Gen|Subject),data=behav_sub,family='binomial',control = glmerControl(optimizer = "bobyqa"), method = "LRT")
b2#ANOVA table
summary(b2)#summary 

library(emmeans)
#post-hoc comparisons to see the effect of Agreement differences between Number and Gender
con3<-emmeans(b2, ~ Agreement*Num_Gen, test = "Tukey")
contrast(con3, interaction ="pairwise")

#post-hoc comparisons to see the effect of Agreement on Number and Gender separately
con4<-emmeans(b2, ~ Agreement|Num_Gen, test = "Tukey")
contrast(con4, interaction ="pairwise")

######VISUALIZATION######### 
#plot model for the significant 2 way-interaction
sjPlot::plot_model(b1, type = "pred", terms = c( "Num_Gen","Agreement"))
#plot model for the 4 way-interaction
sjPlot::plot_model(b1, type = "pred", terms = c("composite_c", "Agreement", "Group","Num_Gen"))



```               
                  
#### Reaction Time Analysis 
```{r}
##Reaction Time Analysis## 

#First we will run a glmer model to do some model diagnostic 
r1<-lmer(RT_log~Agreement*Num_Gen*composite_c*Group+(Agreement+Num_Gen|Subject),data=behav_sub)
summary(r1)

#model diagnostic
sjPlot::plot_model(r1, type='diag')#looks very good 

#run LRT with afex package with the new outlier removed data  
library(afex)
r2<-mixed(RT_log~Agreement*Num_Gen*composite_c*Group+(Agreement+Num_Gen|Subject),data=behav_sub,method = "LRT")
r2#ANOVA table
summary(r2)#summary 

library(emmeans)
#post-hoc comparisons to see the effect of Agreement differences between Number and Gender
con5<-emmeans(r2, ~ Agreement*Num_Gen, test = "Tukey")
contrast(con5, interaction ="pairwise")

#post-hoc comparisons to see the effect of Agreement on Number and Gender separately
con6<-emmeans(r2, ~ Agreement|Num_Gen, test = "Tukey")
contrast(con6, interaction ="pairwise")

######VISUALIZATION######### 
#plot model for the significant 2 way-interaction
sjPlot::plot_model(r1, type = "pred", terms = c( "Num_Gen","Agreement"))
#plot model for the 4 way-interaction
sjPlot::plot_model(r1, type = "pred", terms = c("composite_c", "Agreement", "Group","Num_Gen"))


```  
#### We will now make the ERP plots

```{r}

#Import data and bind all conditions together
#Agrregated Results
NumGr <- read.delim("GA_NumGr_All_Raw Data.txt", header = FALSE, sep = " ", dec = ".")
NumGr$Condition="NumGr"
NumUg <- read.delim("GA_NumUg_All_Raw Data.txt", header = FALSE, sep = " ", dec = ".")
NumUg$Condition="NumUg"
GenGr <- read.delim("GA_GenGr_All_Raw Data.txt", header = FALSE, sep = " ", dec = ".")
GenGr$Condition="GenGr"
GenUg <- read.delim("GA_GenUg_All_Raw Data.txt", header = FALSE, sep = " ", dec = ".")
GenUg$Condition="GenUg"

#Aggregated results split by Native vs. Non-native
NN_GenAgr <- read.delim("AvgGenGr_NNN.txt", header = FALSE, sep = ";", dec = ".")
NN_GenAgr$Agreement="agreement"
NN_GenAgr$Nativeness="Native-NN"
nonNN_GenAgr <- read.delim("AvgGenGr_nonNNN.txt", header = FALSE, sep = ";", dec = ".")
nonNN_GenAgr$Agreement="agreement"
nonNN_GenAgr$Nativeness="nonNative-NN"
NN_GennonAgr <- read.delim("AvgGenUg_NNN.txt", header = FALSE, sep = ";", dec = ".")
NN_GennonAgr$Agreement="non-agreement"
NN_GennonAgr$Nativeness="Native-NN"
nonNN_GennonAgr <- read.delim("AvgGenUg_nonNNN.txt", header = FALSE, sep = ";", dec = ".")
nonNN_GennonAgr$Agreement="non-agreement"
nonNN_GennonAgr$Nativeness="nonNative-NN"
NN_NumnonAgr <- read.delim("AvgNumGr_NNN.txt", header = FALSE, sep = ";", dec = ".")
NN_NumnonAgr$Agreement="non-agreement"
NN_NumnonAgr$Nativeness="Native-NN"
nonNN_NumnonAgr <- read.delim("AvgNumGr_nonNNN.txt", header = FALSE, sep = ";", dec = ".")
nonNN_NumnonAgr$Agreement="non-agreement"
nonNN_NumnonAgr$Nativeness="nonNative-NN"
NN_NumAgr<- read.delim("AvgNumUg_NNN.txt", header = FALSE, sep = ";", dec = ".")
NN_NumAgr$Agreement="agreement"
NN_NumAgr$Nativeness="Native-NN"
nonNN_NumAgr <- read.delim("AvgNumUg_nonNNN.txt", header = FALSE, sep = ";", dec = ".")
nonNN_NumAgr$Agreement="agreement"
nonNN_NumAgr$Nativeness="nonNative-NN"
#rbind all variables
AllCond = rbind(NumGr,NumUg,GenGr,GenUg)
Nativeness_gen = rbind(NN_GenAgr,nonNN_GenAgr, NN_GennonAgr,nonNN_GennonAgr)
Nativeness_num = rbind(NN_NumnonAgr,nonNN_NumnonAgr,NN_NumAgr,nonNN_NumAgr )

# exclude electrodes of no interest
exclude = c("Fp1", "Fp2", "TP9", "TP10", "C3", "C4", "FCz", "FT9", "FT10", "Fp", "O1", "O2", "T7", "T8","x_dir","y_dir","z_dir")
AllCond<-AllCond%>%
  filter(!V1 %in% exclude)

Nativeness_gen<-Nativeness_gen%>%
  filter(!V1 %in% exclude)

Nativeness_num<-Nativeness_num%>%
  filter(!V1 %in% exclude)

#create a vector with numbers from -298 to 1200 with an increment step of 2 - this will be our time column
timepoints <- seq(-298, 1200, by=2)
AllCond <- AllCond[, -c(2,3,4,5)]

#rename columns
names(AllCond)[2:751] <- timepoints
names(AllCond)[1] <- 'Electrode'
names(Nativeness_gen)[2:751] <- timepoints
names(Nativeness_gen)[1] <- 'Electrode'
names(Nativeness_num)[2:751] <- timepoints
names(Nativeness_num)[1] <- 'Electrode'
# transpose wide to long
AllCond_long <- AllCond%>%
gather(key = Time, value = Amplitude,`-298`:`1200`)

Nativeness_gen_long <-Nativeness_gen%>%
gather(key = Time, value = Amplitude,`-298`:`1200`)

Nativeness_num_long <-Nativeness_num%>%
gather(key = Time, value = Amplitude,`-298`:`1200`)
colnames(Nativeness_num_long )
```


```{r}
#######AGGREGATE########
#prepare the aggregate number conditions and electrode Pz for plotting
Num_Pz<-AllCond_long%>%
  filter(Electrode=="Pz"& (Condition=="NumGr"|Condition=="NumUg"))

Num_Pz$Time <- as.numeric(as.vector(Num_Pz$Time))
Num_Pz.plot <- ggplot(data=Num_Pz, aes(x=Time, y=Amplitude, group=Condition)) +
  geom_line(aes(color=Condition))+
  scale_color_brewer(palette = "Set1")+
  theme_classic()+
  geom_vline(xintercept = 0,linetype = "dashed" )+
  geom_hline(yintercept = 0,linetype = "dashed")+
  scale_x_continuous(breaks=seq(-300,1200,300))+
  scale_color_manual(labels = c("Agreement", "Non-Agreement"), values = c("blue", "red"))+
  labs(x = "Time (ms)",y = expression(paste("Amplitude (",mu,"V)")))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16),
        legend.text=element_text(size=12),
        legend.position="bottom")+
  ggtitle("Panel B: Number")+
  ylim(-5,5)


#prepare the aggregate gender condition and electrode Pz for plotting
Gen_Pz<-AllCond_long%>%
  filter(Electrode=="Pz"& (Condition=="GenGr"|Condition=="GenUg"))

Gen_Pz$Time <- as.numeric(as.vector(Gen_Pz$Time))
Gen_Pz.plot <- ggplot(data=Gen_Pz, aes(x=Time, y=Amplitude, group=Condition)) +
  geom_line(aes(color=Condition))+
  scale_color_brewer(palette = "Set1")+
  theme_classic()+
  geom_vline(xintercept = 0,linetype = "dashed" )+
  geom_hline(yintercept = 0,linetype = "dashed")+
  scale_x_continuous(breaks=seq(-300,1200,300))+  
  scale_color_manual(labels = c("Agreement", "Non-Agreement"), values = c("blue", "red"))+
  labs(x = "Time (ms)",y = expression(paste("Amplitude (",mu,"V)")))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16),
        legend.text=element_text(size=12),
        legend.position="bottom")+
  ggtitle("Panel A: Gender")+
  ylim(-5,5)

#Combine two plots
ggarrange(Gen_Pz.plot ,Num_Pz.plot ,
                    ncol = 1, nrow = 2,
           common.legend = TRUE, legend = "right"
          )
  
#######NATIVE vs. NON-NATIVE for Gender and Number##############
#prepare the aggregate number conditions and electrode Pz for plotting
Gen_Nat_Pz<-Nativeness_gen_long %>%
  filter(Electrode=="Pz")%>%
  mutate(Nativeness = str_replace(Nativeness, "-NN", ""))

Gen_Nat_Pz$Time <- as.numeric(as.vector(Gen_Nat_Pz$Time))
Gen_Nat_Pz.plot <- ggplot(data=Gen_Nat_Pz, aes(x=Time, y=Amplitude, group=Agreement)) +
  geom_line(aes(color=Agreement))+
  scale_color_brewer(palette = "Set1")+
  theme_classic()+
  geom_vline(xintercept = 0,linetype = "dashed" )+
  geom_hline(yintercept = 0,linetype = "dashed")+
  scale_x_continuous(breaks=seq(-300,1200,300))+
  scale_color_manual(labels = c("Agreement", "Non-Agreement"), values = c("blue", "red"))+
  labs(x = "Time (ms)",y = expression(paste("Amplitude (",mu,"V)")))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16),
        legend.text=element_text(size=12),
        legend.position="bottom")+
  facet_grid(rows = vars(Nativeness))+
  ggtitle("ERP waveplot of Gender condition split by Nativeness")

#prepare the aggregate gender condition and electrode Pz for plotting
Num_Nat_Pz<-Nativeness_num_long%>%
  filter(Electrode=="Pz")%>%
  mutate(Nativeness = str_replace(Nativeness, "-NN", ""))

Num_Nat_Pz$Time <- as.numeric(as.vector(Num_Nat_Pz$Time))
Num_Nat_Pz.plot <- ggplot(data=Num_Nat_Pz, aes(x=Time, y=Amplitude, group=Agreement)) +
  geom_line(aes(color=Agreement))+
  scale_color_brewer(palette = "Set1")+
  theme_classic()+
  geom_vline(xintercept = 0,linetype = "dashed" )+
  geom_hline(yintercept = 0,linetype = "dashed")+
  scale_x_continuous(breaks=seq(-300,1200,300))+  
  scale_color_manual(labels = c("Agreement", "Non-Agreement"), values = c("blue", "red"))+
  labs(x = "Time (ms)",y = expression(paste("Amplitude (",mu,"V)")))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=16),
        legend.text=element_text(size=12),
        legend.position="bottom")+
  facet_grid(rows = vars(Nativeness))+
  ggtitle("ERP waveplot of Number condition split by Nativeness")

#Combine two plots
fig2<-ggarrange(Gen_Nat_Pz.plot ,Num_Nat_Pz.plot  ,
                    ncol = 1, nrow = 2,
           common.legend = TRUE, legend = "right"
          )

ggsave(filename = "Figure2",device='jpeg', dpi=300)
```





#### Now we will check to see the correlation between behavioural (accuracy) and ERP data 
```{r}
#aggregate individual ERP data 
erp_ind<-erp_all_3%>%
  dplyr::group_by(Subject,Num_Gen,Agreement)%>%
  dplyr::summarise(meanamp = mean(Amplitude))%>%
  spread(Agreement,meanamp)%>%
  mutate(diff_amp = `non-agreement` - agreement)%>%
  select(Subject, Num_Gen, diff_amp)

#aggregate individual acceptance data 
behav_ind<-behav_sub%>%
  dplyr::group_by(Subject,Num_Gen,Agreement)%>%
  dplyr::summarise(meanacc = mean(Accuracy))%>%
  spread(Agreement,meanacc)%>%
  mutate(diff_acc = `non-agreement` - agreement)%>%
  select(Subject, Num_Gen, diff_acc)


#merge two data sets 
ind_data<-merge(erp_ind,behav_ind, by = c("Subject","Num_Gen"))

#subset for gender 
ind_gender<-ind_data%>%
  filter(Num_Gen == "gender")

#subset for number
ind_number<-ind_data%>%
  filter(Num_Gen == "number")

#run correlation for gender
cor.test(ind_gender$diff_amp,ind_gender$diff_acc)

#run correlation for number 
cor.test(ind_number$diff_amp,ind_number$diff_acc)

```





